### 2013-12-06 paper/main.tex
general cleanup, added contents, changed title page
The title page has been changed to only include itself
and the abstract.  On the next page is the contents and
after that is the body of the text.  Before the body
started with the title page and there was no contents.

\usepackage{sectsty}  % \sectionfont
\sectionfont{\normalsize}
\subsectionfont{\normalsize}

@@

\centerline{\Large \textbf{Control System Design Applied to}}
\centerline{\Large \textbf{Idle Stabilization of a Spark Ignition Engine}}
\vspace{0.1in}
\centerline{\normalsize {Jeremiah Mahler}}
\centerline{\small {\href{mailto:jmahler@mail.csuchico.edu}{jmahler@mail.csuchico.edu}} }
\vspace{0.1in}
\centerline{\normalsize {CSU Chico}}
%\centerline{\today}
%\vspace{0.1in}
\centerline{\small \today}
\vspace{0.2in}
\centerline{\LARGE \textbf{DRAFT}}
\vspace{0.2in}

@@

% {{{ abstract
%\pagebreak
%\thispagestyle{empty}
\begin{abstract}
\noindent
The task of maintaining a stable idle for an internal combustion
engine with spark ignition is non-trivial.
Any time an accessory is turned on/off the torque applied to
the engine changes.
And changes in torque will change the engine rpm if the control
inputs are constant.
This paper shows how control system methods can be applied to
the problem of idle stabilization.
Because the engine model is inherently discrete all of the methods
used are also discrete.
Methods include: pole placement, direct design, and
various state space designs.

\end{abstract}
% }}}

% {{{ Engine Model
\section{Engine Model}

@@

While these results were positive it is not obvious whether it is withing
the mechanical limits of a real engine.
In particular the control input should be limited to a range from zero to one.
Further investigation is needed to determine whether these limits
are being exceeded.
There is no doubt, however, that the addition of a controller
improved performance.
If the limits are being exceeded a different set of roots would have to
be chosen which may be less optimal.

@@

The following code has been tested using Octave\autocite{octave},
an open source Matlab clone.

@@

For a given control input with zero torque the stable rpm values reached
are shown in Figure \ref{fig:stable}.
Equation \ref{eq:stable} describes its behavior.
Listing \ref{lst:stable} shows how this was calculated.

>>>>

\usepackage{sectsty}  % \sectionfont
%\sectionfont{\normalsize}
%\subsectionfont{\normalsize}

@@

\vspace*{1.0in}
\centerline{\Large \textbf{Control System Design Applied to}}
\centerline{\Large \textbf{Idle Stabilization of a Spark Ignition Engine}}
\vspace{0.1in}
\centerline{\normalsize {Jeremiah Mahler}}
\centerline{\small {\href{mailto:jmahler@mail.csuchico.edu}{jmahler@mail.csuchico.edu}} }
\vspace{0.1in}
\centerline{\normalsize {California State University Chico}}
\centerline{\small \today}
%\vspace{0.2in}
%\centerline{\LARGE \textbf{DRAFT}}
\vspace{0.5in}

\vfill

\begin{abstract}
\noindent
The task of maintaining a stable idle for an internal combustion
engine with spark ignition is non-trivial.
Any time an accessory is turned on/off the torque applied to
the engine changes.
And changes in torque will change the engine rpm if the control
inputs are constant.
This paper shows how control system methods can be applied to
the problem of idle stabilization.
Because the engine model is inherently discrete all of the methods
used are also discrete.
Methods include: pole placement, direct design, and
various state space designs.
\end{abstract}

\vspace{1.5in}

@@

\clearpage
\tableofcontents

% {{{ Engine Model
\clearpage
\section{Engine Model}

@@

While this result is positive it is not apparent whether it is within
the mechanical limits of a real engine.
In particular the control input should be limited to a range from zero to one.
Further investigation is needed to determine whether these limits
are being exceeded.
There is no doubt, however, that the addition of a controller
improved performance.
If the limits are being exceeded a different set of roots would have to
be chosen which may be less optimal.

@@

\nocite{octave}

@@

For a given control input and zero torque the engine model will
reach stable rpm values as shown in Figure \ref{fig:stable}.
Equation \ref{eq:stable} describes its behavior.
Listing \ref{lst:stable} shows how this was calculated.
